Quantifying social distancing behaviour across Australia in response to COVID-19

### 2020-04-28 manuscript/ms.Rmd
Revert "Revert "adding NBN data section""
This reverts commit 366dca4a323aec58fb9c313b5e039fa604643ad9.
Revert "Revert "Revert "adding NBN data section"""
This reverts commit b22ee3fe8d40380b0dde0e335b7852e5be51f1d9.
adding NBN data section
adding NBN data section - updated
adding timeline draft

>>>>

Full-day NBN data for the period from September 1, 2019, until March 24th, 2020 have been used.

#### Announcement timeline for Australia

Govenrmental controls in response to COVID-19 in Australia started in January 2020. On January 20th, 2020, the Australian government imposed restrictions on flights from the Wuhan region of China. The first case was identified in Australia shortly after, on January 25th. Queensland declared *State of emergency* on January 29th, and travel restrictionsfrom China were imposed on Fenruary 1st. Enforced measures were imposed from March 16th, with a ban on non-essential gatherings, with Victoria declaring a *State of emergency* on the same day, and closing schools from March 22nd. From the 22th of March, Stage 1 restricitons were mandated (closures of pubs, restaurants, except takeaway, and adivsing on social distancing). This was escalated to Stage 2 from March 26th, with mandatory social distancing and closures of museums, galleries, many additional services. On March 31st, Stage 3 restrictions were imposed, with enforcdeable stay at home measures.
